U.S. Labour Market Resilience

### 2024-03-17 paper/paper.qmd
draw a little graph for now

data <- read.csv(here::here("data/analysis_data/cleaned_data.csv"))
# Get rid of the first letter X for each of the years
colnames(data)[1] <- "work_hours"
colnames(data) <- gsub("X", "", colnames(data))

@@

>>>>

data <- read.csv(here::here("data/analysis_data/cleaned_data.csv"))
# Get rid of the first letter X for each of the years
colnames(data) <- gsub("X", "", colnames(data))

@@

```{r}
#| label: fig-hour-working-percentage
#| fig-cap: Average Working Hours Percentages 
#| echo: false
#| warning: false
#| message: false
#| 
data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
data <- data[c(2:ncol(data))]
# Get rid of the first letter X for each of the years
colnames(data) <- gsub("X", "", colnames(data))
work_hours <- rep(data$work_hours,35)
years <- colnames(data)[2:36]
years <- rep(years,each=7)

responses <- unname(unlist(data[c(2:36)]))

data_long <- data.frame(cbind(work_hours,years,responses))
Totals <- filter(data_long, work_hours == "Total")
Subtotals <- filter(data_long, work_hours == "No Response")
Totals$responses <- as.numeric(Totals$responses)
Subtotals$responses <- as.numeric(Subtotals$responses)
Subtotals <- mutate(Subtotals, subtotal = Totals$responses - Subtotals$responses)

data_perc <- data_long %>%  filter(years>=1993) %>% 
  filter(work_hours != "Total") %>%
  filter(work_hours != "No Response")

# Generate heatmap
generate_heatmap <- function(
    ggplot_data,
    xlabel = NULL,
    ylabel = NULL,
    position = NULL,
    angle = 45,
    hjust = 1,
    vjust = 1
) {

  ggplot_data +
    geom_tile() +
    scale_fill_gradient2(low = "white", high = "darkblue", guide = "colorbar") +
    theme(
      axis.text.x = element_text(angle = angle, vjust = vjust, hjust = hjust)
    ) +
    theme(legend.position = position) +
    labs(
      x = xlabel,
      y = ylabel,
    )
}

ggplot_data <- inner_join(data_perc, Subtotals, 
                          by = c("years"))
ggplot_data$responses.x <- as.numeric(ggplot_data$responses.x)
ggplot_data <- mutate(ggplot_data,Percentage = responses.x/subtotal)

generate_heatmap(
  ggplot_data |>
    ggplot(aes(x = years, y = work_hours.x, fill = Percentage)),
  xlabel = "Year of Data Collected",
  ylabel = "Number of Hours Worked Last Week"
)
